Through the eyes of the teacher

### 2021-06-21 01_studies/02_2020_Aperol-pilot/questionnaire data/gregor beispiele/eval_wise1920/evaluation_final_WS1920.Rmd
SRI / Erhebungsprotokoll / Versuchsleitungsmanual

# THIS IS THREE PLOTS IN ONE - Hooray!
# as we call three plots and two dataframes, the first line requires dummy NULL entries 
modul.plot <- ggplot(data = NULL, mapping = aes(NULL)) +
  # then we call a violin from all data, trim = cut at limits, adjust = makes slender 
  geom_violin(data = Modul.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5),
              mapping = aes(x=item, y = value))+
  # a jitter plot Alle vs Individual (Teilnehmende), 
  geom_jitter(modul.plot.data, width = 0.1, inherit.aes = FALSE, size = 1,
              mapping = aes(x = item, y = value, colour = Teilnehmende))+
  # mean and SD via geom pointrange for all and individual (Teilnehmende)
  geom_crossbar(data = modul.plot.sd, position = "dodge", width = 0.5,
                aes(x=item, y = mean, ymin = mean-se, ymax = mean+se, colour = Teilnehmende))+
  # we can't make the violin transparent, so we change the bakground to white
  theme_light() +
  theme(legend.position="bottom") +
  # axis limits from 1 through 5
  ylim(1,5)+
  # label the plot, also here we have to call the data to get the item names
  labs(data = modul.plot.data, y = "Ausprägung", x = "Item",
       title="Modulbewertung",
       subtitle="Verteilung der Werte je Item und Mittelwerte der Items")
modul.plot

>>>>

# THIS IS THREE PLOTS IN ONE - Hooray!
# as we call three plots and two dataframes, the first line requires dummy NULL entries 
modul.plot <- ggplot(data = NULL, mapping = aes(NULL)) +
  # then we call a violin from all data, trim = cut at limits, adjust = makes slender 
  geom_violin(data = Modul.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5),
              mapping = aes(x=item, y = value))+
  # a jitter plot Alle vs Individual (Teilnehmende), 
  geom_jitter(modul.plot.data, width = 0.1, inherit.aes = FALSE, size = 1,
              mapping = aes(x = item, y = value, colour = Teilnehmende))+
  # mean and SD via geom pointrange for all and individual (Teilnehmende)
  geom_crossbar(data = modul.plot.sd, position = "dodge", width = 0.5,
                aes(x=item, y = mean, ymin = mean-se, ymax = mean+se, colour = Teilnehmende))+
  # we can't make the violin transparent, so we change the background to white
  theme_light() +
  theme(legend.position="bottom") +
  # axis limits from 1 through 5
  ylim(1,5)+
  # label the plot, also here we have to call the data to get the item names
  labs(data = modul.plot.data, y = "Ausprägung", x = "Item",
       title="Modulbewertung",
       subtitle="Verteilung der Werte je Item und Mittelwerte der Items")
modul.plot

### 2021-06-21 02_paper/schrott/paper_1_supplement.tex
SRI / Erhebungsprotokoll / Versuchsleitungsmanual

\begin{figure}

{\centering \includegraphics{./pictures/datacollection}

\caption{Example for set up during a mini-lesson}\label{fig:datacollection}
\end{figure}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Classroom management
\item
  Positive climate and motivation
\item
  Clarity and structuredness
\item
  Activation and support
\item
  Presence: posture/gaze
\item
  Presence: voice
\item
  Presence: verbal and non-verbal intervention
\item
  Natural behaviour
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Classroom management
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/classroom management line plots-1.pdf}
  \newpage
\item
  Positive climate and motivation
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Positive climate and motivation line plots-1.pdf}
  \newpage
\item
  Clarity and structuredness
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Clarity and structuredness line plots-1.pdf}
  \newpage
\item
  Activation and support
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Activation and support line plots-1.pdf}
  \newpage
\end{enumerate}

\begin{figure}

{\centering \includegraphics{./pictures/presenceposturegaze}

\caption{(5) Presence: posture/gaze}\label{fig:presenceposturegaze}
\end{figure}

\begin{figure}

{\centering \includegraphics{./pictures/presencevoice}

\caption{(6) Presence: voice}\label{fig:presencevoice}
\end{figure}
\newpage

\begin{figure}

{\centering \includegraphics{./pictures/presenceverbalnonverbalintervention}

\caption{(7) Presence: verbal and non-verbal intervention}\label{fig:presenceverbalnonverbalintervention}
\end{figure}
\newpage

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  Natural behaviour
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Natural behaviour line plots-1.pdf}
  \newpage
  In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/boxplot scales-1.pdf}
  \newpage
  Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment. The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
\end{enumerate}

\includegraphics{paper_1_supplement_with_presence_files/figure-latex/Duration speaking time-1.pdf}
\newpage

>>>>

(ref:data\_collection-caption) Example for the set up during a mini-lesson

\textbackslash begin\{figure\}

\{\centering \includegraphics{./pictures/data_collection}

\}

\textbackslash caption\{(ref:data\_collection-caption)\}(\#fig:data collection)
\textbackslash end\{figure\}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Classroom management
\item
  Positive climate and motivation
\item
  Clarity and structuredness
\item
  Activation and support
\item
  Presence: posture and gaze
\item
  Presence: voice
\item
  Presence: verbal and non-verbal intervention
\item
  Natural behaviour
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\item
  Classroom management
  \includegraphics{paper_1_supplement_files/figure-latex/classroom management line plots-1.pdf}
\item
  Positive climate and motivation
  \includegraphics{paper_1_supplement_files/figure-latex/Positive climate and motivation line plots-1.pdf}
\item
  Clarity and structuredness
  \includegraphics{paper_1_supplement_files/figure-latex/Clarity and structuredness line plots-1.pdf}
\item
  Activation and support
  \includegraphics{paper_1_supplement_files/figure-latex/Activation and support line plots-1.pdf}
\item
  Presence: posture and gaze
  \includegraphics{paper_1_supplement_files/figure-latex/Presence: posture and gaze line plots-1.pdf}
\item
  Presence: voice
  \includegraphics{paper_1_supplement_files/figure-latex/Presence: voice line plots-1.pdf}
\item
  Presence: verbal and non-verbal intervention
  \includegraphics{paper_1_supplement_files/figure-latex/Presence: verbal and non-verbal intervention line plots-1.pdf}
\item
  Natural behaviour
  \includegraphics{paper_1_supplement_files/figure-latex/Natural behaviour line plots-1.pdf}
\end{enumerate}

In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
\includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}

Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment. The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.

\includegraphics{paper_1_supplement_files/figure-latex/Duration speaking time-1.pdf}

### 2021-06-21 02_paper/schrott/paper_1_supplement_new_table.Rmd
SRI / Erhebungsprotokoll / Versuchsleitungsmanual

quest.plot <- quest.raw.data %>%
  ggplot(aes(x=scale, y=value, fill=scale)) +
    geom_boxplot() +
    scale_x_discrete(guide = guide_axis(angle = 70)) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    facet_grid(~group)+
    ggtitle("Boxplot with individual points for all scales") +
    xlab("")
quest.plot

@@

```{r GRItable, echo = FALSE}

# prepare data (selected from questionnaire data)
et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)

# converting integer to numeric
et.raw.data <- et.raw.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
                                       )

# calculate the GRI 
# create a basic table (tibble) using tidyverse functions
et.raw.table <- et.raw.data %>%
  group_by(Participant, Variable) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Fixation Duration" = Total_duration_of_whole_fixations,
            "M Duration Fixation" = Average_duration_of_whole_fixations,
            "TOI" = Duration_of_interval,
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)

# format and insert table in manuscript
apa_table(
  et.raw.table,
  caption = "Number and Duration (in msec) of Fixations",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

>>>>

quest.plot <- quest.raw.data %>%
  ggplot(aes(x=scale, y=value, fill=scale)) +
    geom_boxplot() +
    scale_x_discrete(guide = guide_axis(angle = 70)) +
    geom_jitter(color="black", size=0.4, alpha=0.5) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)) +
    facet_grid(~group)+
    ggtitle("Boxplot with individual points for all scales") +
    xlab("")
quest.plot

@@

```{r GRItable1, echo = FALSE}

# prepare data (selected from questionnaire data)
et.toi.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", dec=",", sep="\t", header=T)

# converting integer to numeric
et.toi.data <- et.toi.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations))

# calculate the GRI 
# create a basic table (tibble) using tidyverse functions
et.toi.table1 <- et.toi.data %>%
  group_by(TOI) %>%
  summarise("ID" = Participant,
            "Group" = Variable1,
            "Duration TOI ms" = Duration_of_interval,
            "M Duration Fixation" = mean(Total_duration_of_whole_fixations),
            "Number Fixation" = Number_of_whole_fixations,
            "Time TOI Duration" = Duration_of_interval/mean(Total_duration_of_whole_fixations),
            "Old GRI" = mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations,
            "New GRI" = (Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations)

# format and insert table in manuscript
apa_table(
  et.toi.table1,
  caption = "GRI",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

```{r GRItable2, echo = FALSE}

# prepare data (selected from questionnaire data)
et.toi.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", dec=",", sep="\t", header=T)

# converting integer to numeric
et.toi.data <- et.toi.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations))

# calculate the GRI 
# create a basic table (tibble) using tidyverse functions
et.toi.table2 <- et.toi.data %>%
  group_by(Variable1, TOI) %>%
  rename("Group" = Variable1) %>%
  summarise("M Fixation Duration" = mean(Total_duration_of_whole_fixations),
            "M Number Fixation" = mean(Number_of_whole_fixations),
            "M TOI" = mean(Duration_of_interval),
            "M Old GRI" = mean(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
            "SD Old GRI" = sd(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
            "M New GRI" = mean((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations),
            "SD New GRI" = sd((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations))

# format and insert table in manuscript
apa_table(
  et.toi.table2,
  caption = "GRI",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

```{r GRItable3, echo = FALSE}

# prepare data (selected from questionnaire data)
et.toi.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", dec=",", sep="\t", header=T)

# converting integer to numeric
et.toi.data <- et.toi.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations))

# calculate the GRI 
# create a basic table (tibble) using tidyverse functions
et.toi.table3 <- et.toi.data %>%
  group_by(Variable1) %>%
  rename("Group" = Variable1) %>%
  summarise("M Fixation Duration" = mean(Total_duration_of_whole_fixations),
            "M Number Fixation" = mean(Number_of_whole_fixations),
            "M TOI" = mean(Duration_of_interval),
            "M Old GRI" = mean(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
            "SD Old GRI" = sd(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
            "M New GRI" = mean((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations),
            "SD New GRI" = sd((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations))

# format and insert table in manuscript
apa_table(
  et.toi.table3,
  caption = "GRI",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )
